---
title: "CodeBook"
author: "Onyeka Enwerem"
date: "December 23, 2016"
output: html_document
---

Codebook
========
Codebook was generated on `r as.character(Sys.time())` 

Variable list and descriptions
------------------------------

Variable name  | Description
----------------|------------
subject        | ID of the subject who performed the activity for each window sample. Its range is from 1 to 30.
activity       | Activity name
domain         | Feature: Time domain signal or frequency domain signal (Time or Freq)
instrument     | Feature: Measuring instrument (Accelerometer or Gyroscope)
acceleration   | Feature: Acceleration signal (Body or Gravity)
variable       | Feature: Variable (Mean or SD)
jerk           | Feature: Jerk signal
magnitude      | Feature: Magnitude of the signals calculated using the Euclidean norm
axis           | Feature: 3-axial signals in the X, Y and Z directions (X, Y, or Z)
count          | Feature: Count of data points used to compute `average`
average        | Feature: Average of each variable for each activity and each subject

Dataset structure
-----------------
```{r eval=TRUE, echo=TRUE} 
library(knitr)
```


```{r eval=TRUE, echo=TRUE, include=TRUE} 
str(dtTidy)
```

List the key variables in the data table
----------------------------------------

```{r}
key(dtTidy)
```

Show a few rows of the dataset
------------------------------

```{r}
dtTidy
```


Summary of variables
--------------------

```{r}
summary(dtTidy)
```


